Objectification in Action: Self- and Other-Objectification in Same-gender Interactions

### 2020-08-03 Final_Manuscript.tex
commit

\documentclass[man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Objectification in Action: Self- and Other-Objectification in Same-gender Interactions},
            pdfauthor={Randi L. Garcia, Kat Kyuchukova, Asha Hinson, \& Laneé Jung},
            pdfkeywords={keywords},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

\shorttitle{Objectification in Action}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} Department of Psychology, Smith College\\\textsuperscript{2} Program in Statistical and Data Sciences, Smith College}
\keywords{keywords}
\usepackage{csquotes}
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\abstract{
Empirical evidence has only found links between objectification,
self-objectification, and negative outcomes for woman within
interpersonal interactions between male-female pairs. The purpose of the
present study was to extend past research and consider the relationships
between such valuable phenomena and their effects on authenticity within
interactions between female pairs. Woman were brought into the
laboratory and interacted in same-sex dyads. Dyadic analysis was
utilized to detect whether partners' objectification of each other
affected state self-objectification, and the resulting feelings of
comfort and authenticity during the interaction. After the interaction,
participants completed a questionnaire which measured many constructs
including cognitive performance, career aspirations, and relationship
agency. Results revealed no significant relationship between
self-objectification and authenticity. Further, although there were
significantly negative effects on career aspirations and relationship
agency resulting from a lack of relationship authenticity, there was no
evidence that this is due to feelings of sexual objectification. The
significant partner effect of objectification on actor
self-objectification suggests that women being objectified by other
women still results in feelings of self-objectification, and such
research has powerful implications for the ways that women interact in
both sexual and non-sexual settings. AUTHOR NOTE: mention Clark trigram
coders Hannah et al.

@@

Roberts and Fredrickson (1997) Objectification Theory, suggests that
women are objectified in interpersonal encounters, and that the effect
might be strongest from men, but possibly also from women. Psychological
researchers studying the sexual objectification of women, and the
resulting self-objectification that follows, have in recent years
explored the interpersonal process of the objectification -
self-objectification link (CITE INTERPERSONAL PROCESS LINKS LITERATURE).
For example, in a face-to-face mixed-gender dyadic study, Garcia,
Earnshaw, and Quinn (2016) found that men's reported objectification of
their female interaction partner during an interaction was associated
with increased self-objectification reported by their partner. Gervais,
Sáez, Riemer, and Klein (2020) has reviewed the literature on
interpersonal self-objectification and has organized the the process in
a theoretical model called the SIMO, but this model is only relevant for
mixed-gender encounters. Although there is ample evidence that women
objectify other women (Loughnan et al., 2015a; Puvia \& Vaes, 2013),
there is currently no studies investigating the process of interpersonal
objectification same-gender interactions. Does objectification by a
female interaction partner have the same downstream negative
consequences as being objectified by a male interaction partner? For
example, perhaps women could be amplifying each others'
self-objectification as they get ready to go out for the night,
\emph{before} the theoretical encounters with men outlined in Gervais et
al. (2020) occur.

\subsection{Self-Objectification}\label{self-objectification}

Self-objectification is a multidimensional process that accounts for the
cognitive mechanism that translates experiences of sexualization at the
cultural level (Loughnan et al., 2015a) to psychological (e.g., anxiety,
self-esteem, authenticity, motivational states) and behavioral
(cognitive performance, body monitoring) features of mental health and
well-being at the individual level (Calogero, Tantleff-Dunn, \&
Thompson, 2011; Moradi \& Huang, 2008). Calogero et al. (2011) proposes
that the construct of self-objectification can be conceptualized as a
learned trait. Furthermore, it can also be elicited momentarily, through
the media, for example, with sexualized images in movies and magazines
(Morry \& Staska, 2001), which can lead to a state of
self-objectification (Bernard, Legrand, \& Klein, 2018; Calogero et al.,
2011; Moradi \& Huang, 2008). Being objectified by another person and
possessing trait-level self-objectification (TSO) may interact to
influence experiences of feeling like a body, or state
self-objectification (SSO) (B. L. Fredrickson, Roberts, Noll, Quinn, \&
Twenge, 1998, Garcia et al. (2016)). Does this habit
self-objectification lead women to also objectify other women, possibly
to compare oneself?

\subsection{Women Objectifying Women}\label{women-objectifying-women}

Past research has focused on men's objectifying behaviors, with little
attention to the role that women may also play in enacting
objectification of women. Hill and Fischer (2008) assessed women's
experiences of objectification from men separately from women's
experiences of objectification from women and found that women may be
socialized not only to see themselves as objects but perhaps to see
other women as objects as well (THEY DIDN'T DETERMINE THIS IN PERSON).
Some studies have found that women objectify other women to a greater
extent than they objectify men (Loughnan et al., 2015a). Women objectify
(dehumanized) sexualized targets presented as images (Puvia \& Vaes,
2013), but we know next to nothing about interpersonal sexual
objectification among women and what the immediate effects might be.
Further, do women objectify non-sexualized women they are interacting
with? What might be different for same-gender interactions? Harsey and
Zurbriggen (2020) found that self-objectification was related to the
objectification of women to a similar degree for men and women
participants, although men scored high than women on a measure of belief
that objectification of women is natural for men. ASK RANDI-WE KNOW
OBJECTIFICATION HAS MORE ADVERSE CONSEQUENCES FOR WOMEN THAN MEN
(Gervais, Vescio, \& Allen, 2011; Moradi \& Huang, 2008; Saguy, Quinn,
Dovidio, \& Pratto, 2010)\ldots{}MENTION THAT\ldots{}HOWEVER DOES WOMEN
OBJECT WOMEN TO A GREATER EXTENT THAN MEN MATTER MORE?\ldots{}STILL
TRYING TO FIGURE THAT OUT? ADDITIONALLY Strelan and Hargreaves (2005)
FOUND THAT THE MORE WOMEN SELF-OBJECTIFY, THE MORE THEY OBJECTIFY OTHER
WOMEN.

\subsection{Interpersonal
Objectification}\label{interpersonal-objectification}

SIMO model and literature review (Gervais et al., 2020). Studies have
shown that within social encounters women are gazed at more than men
(Briton \& Hall, 1995), often times feel \enquote{looked at} within
interpersonal interactions (Argyle \& Williams, 1969; Miles-McLean et
al., 2015), and will more than likely internalize the objectifying gaze
on physical self (Puvia \& Vaes, 2013; Young, 1979). Moreover, perhaps
the most adverse effect of objectifying treatment is that it effectively
socializes girls and women to treat themselves as objects to be looked
at and evaluated, an effect termed self-objectification (Bartky, 1990;
Berger, Cohen, \& Zelditch Jr, 1972; B. L. Fredrickson et al., 1998). We
don't know about women-on-women interpersonal objectification. What
might be different?

Self-objectification has been found to occur after a mere relationship
prime among women (Sanchez \& Broccoli, 2008) because in our culture
women need to look attractive to obtain and maintain successful
relationship, thus, the ``college relationships condition may heighten
self-objectification and the evaluation of other women in a sexualized
way. Among heterosexual male and female college students, self-
objectification has been found to be positively associated with the
extent to which they objectify their romantic partners (Zurbriggen,
Ramsey, \& Jaworski, 2011). Researchers have also studied interpersonal
objectification and self-objectification in romantic relationships
(Strelan \& Pagoudis, 2018). Evidence is mixed, and women can sometimes
have positive outcomes from appearance valuation within the context of
an established romantic relationship and they experience less SSO after
appearance comments within romantic relationships (Meltzer, 2020), less
is known about first dates. But this literature is also only about
heterosexual relationships. A recent study has investigated the effect
of self-objectification on the reduction of relationship building skills
in general (including same-sex friendships) {[}CITE PWQ paper I
reviewed, Yoder editor{]}. Empirical evidence reveals that
objectification manifests through inauthenticity in romantic
relationships (Brunell et al., 2010), adverse attitudes in regard to
career aspirations, and a decrease in concentration and impairment in
female cognitive performance (Kahalon, Shnabel, \& Becker, 2018; D. M.
Quinn, Chaudoir, \& Kallen, 2011). Both romantic relationships and
relationships in general have been studies in the context of
objectification, but neither of these literatures have investigated
specifically same-gender relationships.

There is evidence that the experience of state self-objectification in
mixed-gender contexts (stranger and romantic) and within the self in any
moment (trying on a swimsuit) has negative consequences, but what about
in the context of interaction with other women? Is the
self-objectification experience in mixed-gender interactions the same as
that experienced in same-gender interactions? The ample research
demonstrating that the male gaze has a particularly detrimental effect
would suggest no (Gay \& Castano, 2010; Gervais, Vescio, \& Allen, 2011;
Saguy, Quinn, F Dovidio, \& Pratto, 2010, Calogero (2004); Yilmaz \&
Bozo, 2019). Women do objectify other women (Harsey \& Zurbriggen, 2020;
Loughnan et al., 2015a; Puvia \& Vaes, 2013), but when they do it, does
it lead to self-objectification in the same way men's objectification of
women does (Garcia et al., 2016)? If so, does the self-objectification
experienced in these same-gender interactions have the same negative
consequences for authenticity in that interaction?

\subsection{Interpersonal Objectification and
Authenticity}\label{interpersonal-objectification-and-authenticity}

There is some evidence that reduced authenticity is a consequence of
self-objectification in the moment {[}Garcia et al. (2016); again CITE
PWQ paper I reviewed, Yoder editor{]}. This link has been justified by
the literature on stigmatized-stigmatizer interactions (CITE LITERATURE
DIDN'T COME ACROSS THIS), viewing the experience of being objectified in
an interaction as an identity threat situation (MAYBE CITE MILES-MCLEAN
PAPER \enquote{STOP LOOKING AT ME!}). When a woman is objectified by a
man, and then experiences self-objectification, this intergroup
encounter might trigger identitiy threat, but is the same negative
consequence present when a woman is objectified by another woman?
woman-woman interpersonal objectification processes might diverge from
this process. One the one hand, she may not be having the same negative
consequences the cascade from situations that threated group-based
identity (Deaux \& Major, 1987; Dovidio, Hebl, Richeson, \& Shelton,
2006; M. R. Hebl \& Dovidio, 2005), but feeling like a body, rather than
a full human, in an interaction may be enough to reduce feelings of
authenticity and social competence, regardless of the gender of the
objectifyer {[}Tolman, Impett, Tracy, and Michael (2006); PWQ paper I
reviewed, Yoder editor{]}. I DONT KNOW WHERE THIS PAPER IS? ASK RANDI
ABOUT IDENTITY\_THREAT PAPERS

\subsection{The Current Study}\label{the-current-study}

In the current study, we sought to examine what occurs during an
interaction in which one or both partners are objectifying each other,
similarly to Garcia et al. (2016), but between same-sex female
interpersonal interactions. Moreover, the current study uses a
face-to-face interaction paradigm and dyadic data analysis techniques to
examine the effects for both women simultaneously. We expected to
replicate the results found in Garcia et al. (2016). We predicted that
being objectified by one's interaction partner would lead to
self-objectification, which in turn would lead to feelings of
inauthenticity, then reduced feelings of agency in romantic
relationships, reduced career aspiration, and reduced cognitive
performance. Specifically, we expected to find a positive relationship
between other-objectification by one's partner and state
self-objectification. We also expect to find a negative relationship
between self-state objectification and interaction authenticity, and
that interaction authenticity will be positively related to cognitive
performance, relationship agency, and career aspirations.

Puvia and Vaes (2013) would alternatively predict that women's tendency
to self-objectify (TSO) leads them to objectify other women
(\ldots{}well, dehumanize a sexualized woman, but also Strelan and
Hargreaves (2005) would predict the TSO-\textgreater{}SOO link and
Harsey and Zurbriggen (2020) too), and this is mediated by the woman's
own state self-objectification (SSO). So we also tested this as a
possible alternative model.

\section{Methods}\label{methods}

\subsection{Procedure}\label{procedure}

The procedure used was identical to that in Garcia et al. (2016), except
for the instructions that the participants were given. In brief, that
methodology is that each participant arrived at the laboratory and were
then led into separate cubicles to prevent any communication between the
participants before the interaction. In addition, each participant was
screened for prior acquaintance to confirm that they had not met prior
to the study. They were asked to sign the consent form to participate,
and the study was described as follows: \enquote{This is a study looking
at how students form different types of relationships at college.} A
prompt on the computer screen told the participants that they were
assigned to the \enquote{College Relationships} condition and gave the
following instructions:

@@

\subsection{Combined Samples}\label{combined-samples}

@@

\subsection{Post interaction Measures}\label{post-interaction-measures}

@@

\subsubsection{Cognitive Performance}\label{cognitive-performance}

@@

\subsubsection{State
Other-Objectification}\label{state-other-objectification}

@@

\subsubsection{Interaction Authenticity}\label{interaction-authenticity}

@@

\subsubsection{State
Self-Objectification}\label{state-self-objectification}

@@

\subsubsection{Relationship Agency}\label{relationship-agency}

@@

\subsubsection{Career Aspirations}\label{career-aspirations}

To conceptualize participants' career aspirations after the interaction,
we used the 10-item adaptation of P. Gray and M. OBrien (2007)'s Career
Aspiration Scale employed in Garcia et al. (2016), which asked
participants to consider how true 10 statements were in regard to their
future careers on a scale from 0 (not at all true of me) to 4 (very true
of me). Items include \enquote{I hope to become a leader in my career
field} and \enquote{I hope to move up through any organization or
business I work in.} Items were fairly reliable (\(\alpha\) = 0.73 for
Sample 1, \(\alpha\) = 0.80 for Sample 2).

\subsubsection{Trait
Self-Objectification}\label{trait-self-objectification}

Trait self-objectification (TSO) was assessed using the
Self-Objectification Questionnaire (B. L. Fredrickson et al., 1998; M.
Noll \& L. Fredrickson, 1998), which evaluates the extent to which
individuals view their bodies in observable versus non-observable ways.
The questionnaire asked participants to rank order both appearance and
functional aspects of their bodies, from 1 (least important) to 10 (most
important), with respect to physical self-concepts. Of the ten body
attributes, five of the items were appearance-based (weight, sex appeal,
physical attractiveness, firm/sculpted muscles and body measurements),
and five of the items were competence-based (strength, physical
coordination, energy level, health and physical fitness). Difference
scores were computed by subtracting the sum of the 5 functional
aspects/competence attributes (e.g., health, strength) from the sum of
the 5 physical self-concepts/appearance attributes (e.g., physical
attractiveness, weight), and all measures were multiplied by -1, as was
done in Garcia et al. (2016), so that positive scores indicated greater
TSO.

\section{Results}\label{results}

\subsection{Data analysis}\label{data-analysis}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Objectification in Action: Self- and Other-Objectification in Same-gender Interactions},
  pdfauthor={Randi L. Garcia, Kat Kyuchukova, Asha Hinson, \& Laneé Jung},
  pdfkeywords={keywords},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\shorttitle{Objectification in Action}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} Department of Psychology, Smith College\\\textsuperscript{2} Program in Statistical and Data Sciences, Smith College}
\keywords{keywords}
\usepackage{csquotes}
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\abstract{
Empirical evidence has only found links between objectification, self-objectification, and negative outcomes for woman within interpersonal interactions between male-female pairs. The purpose of the present study was to extend past research and consider the relationships between such valuable phenomena and their effects on authenticity within interactions between female pairs. Woman were brought into the laboratory and interacted in same-sex dyads. Dyadic analysis was utilized to detect whether partners' objectification of each other affected state self-objectification, and the resulting feelings of comfort and authenticity during the interaction. After the interaction, participants completed a questionnaire which measured many constructs including cognitive performance, career aspirations, and relationship agency. Results revealed no significant relationship between self-objectification and authenticity. Further, although there were significantly negative effects on career aspirations and relationship agency resulting from a lack of relationship authenticity, there was no evidence that this is due to feelings of sexual objectification. The significant partner effect of objectification on actor self-objectification suggests that women being objectified by other women still results in feelings of self-objectification, and such research has powerful implications for the ways that women interact in both sexual and non-sexual settings. AUTHOR NOTE: mention Clark trigram coders Hannah et al.~

@@

Roberts \& Fredrickson (1997) Objectification Theory, suggests that women are objectified in interpersonal encounters, and that the effect might be strongest from men, but possibly also from women. Psychological researchers studying the sexual objectification of women, and the resulting self-objectification that follows, have in recent years explored the interpersonal process of the objectification - self-objectification link (CITE INTERPERSONAL PROCESS LINKS LITERATURE). For example, in a face-to-face mixed-gender dyadic study, Garcia, Earnshaw, \& Quinn (2016) found that men's reported objectification of their female interaction partner during an interaction was associated with increased self-objectification reported by their partner. Gervais, Sáez, Riemer, \& Klein (2020) has reviewed the literature on interpersonal self-objectification and has organized the the process in a theoretical model called the SIMO, but this model is only relevant for mixed-gender encounters. Although there is ample evidence that women objectify other women (Loughnan et al., 2015a; Puvia \& Vaes, 2013), there is currently no studies investigating the process of interpersonal objectification same-gender interactions. Does objectification by a female interaction partner have the same downstream negative consequences as being objectified by a male interaction partner? For example, perhaps women could be amplifying each others' self-objectification as they get ready to go out for the night, \emph{before} the theoretical encounters with men outlined in Gervais et al. (2020) occur.

\#\#Self-Objectification
Self-objectification is a multidimensional process that accounts for the cognitive mechanism that translates experiences of sexualization at the cultural level (Loughnan et al., 2015a) to psychological (e.g., anxiety, self-esteem, authenticity, motivational states) and behavioral (cognitive performance, body monitoring) features of mental health and well-being at the individual level (Calogero, Tantleff-Dunn, \& Thompson, 2011; Moradi \& Huang, 2008). Calogero et al. (2011) proposes that the construct of self-objectification can be conceptualized as a learned trait. Furthermore, it can also be elicited momentarily, through the media, for example, with sexualized images in movies and magazines (Morry \& Staska, 2001), which can lead to a state of self-objectification (Bernard, Legrand, \& Klein, 2018; Calogero et al., 2011; Moradi \& Huang, 2008). Being objectified by another person and possessing trait-level self-objectification (TSO) may interact to influence experiences of feeling like a body, or state self-objectification (SSO) (Fredrickson, Roberts, Noll, Quinn, \& Twenge, 1998, p. Garcia et al. (2016)). Does this habit self-objectification lead women to also objectify other women, possibly to compare oneself?

\#\#Women Objectifying Women
Past research has focused on men's objectifying behaviors, with little attention to the role that women may also play in enacting objectification of women. Hill \& Fischer (2008) assessed women's experiences of objectification from men separately from women's experiences of objectification from women and found that women may be socialized not only to see themselves as objects but perhaps to see other women as objects as well (THEY DIDN'T DETERMINE THIS IN PERSON).
Some studies have found that women objectify other women to a greater extent than they objectify men (Loughnan et al., 2015a). Women objectify (dehumanized) sexualized targets presented as images (Puvia \& Vaes, 2013), but we know next to nothing about interpersonal sexual objectification among women and what the immediate effects might be. Further, do women objectify non-sexualized women they are interacting with? What might be different for same-gender interactions? Harsey \& Zurbriggen (2020) found that self-objectification was related to the objectification of women to a similar degree for men and women participants, although men scored high than women on a measure of belief that objectification of women is natural for men. ASK RANDI-WE KNOW OBJECTIFICATION HAS MORE ADVERSE CONSEQUENCES FOR WOMEN THAN MEN (Gervais, Vescio, \& Allen, 2011; Moradi \& Huang, 2008; Saguy, Quinn, Dovidio, \& Pratto, 2010)\ldots MENTION THAT\ldots HOWEVER DOES WOMEN OBJECT WOMEN TO A GREATER EXTENT THAN MEN MATTER MORE?\ldots STILL TRYING TO FIGURE THAT OUT? ADDITIONALLY Strelan \& Hargreaves (2005) FOUND THAT THE MORE WOMEN SELF-OBJECTIFY, THE MORE THEY OBJECTIFY OTHER WOMEN.

\#\#Interpersonal Objectification
SIMO model and literature review (Gervais et al., 2020). Studies have shown that within social encounters women are gazed at more than men (Briton \& Hall, 1995), often times feel \enquote{looked at} within interpersonal interactions (Argyle \& Williams, 1969; Miles-McLean et al., 2015), and will more than likely internalize the objectifying gaze on physical self (Puvia \& Vaes, 2013; Young, 1979). Moreover, perhaps the most adverse effect of objectifying treatment is that it effectively socializes girls and women to treat themselves as objects to be looked at and evaluated, an effect termed self-objectification (Bartky, 1990; Berger, Cohen, \& Zelditch Jr, 1972; Fredrickson et al., 1998). We don't know about women-on-women interpersonal objectification. What might be different?

Self-objectification has been found to occur after a mere relationship prime among women (Sanchez \& Broccoli, 2008) because in our culture women need to look attractive to obtain and maintain successful relationship, thus, the "college relationships condition may heighten self-objectification and the evaluation of other women in a sexualized way. Among heterosexual male and female college students, self- objectification has been found to be positively associated with the extent to which they objectify their romantic partners (Zurbriggen, Ramsey, \& Jaworski, 2011). Researchers have also studied interpersonal objectification and self-objectification in romantic relationships (Strelan \& Pagoudis, 2018). Evidence is mixed, and women can sometimes have positive outcomes from appearance valuation within the context of an established romantic relationship and they experience less SSO after appearance comments within romantic relationships (Meltzer, 2020), less is known about first dates. But this literature is also only about heterosexual relationships. A recent study has investigated the effect of self-objectification on the reduction of relationship building skills in general (including same-sex friendships) {[}CITE PWQ paper I reviewed, Yoder editor{]}. Empirical evidence reveals that objectification manifests through inauthenticity in romantic relationships (Brunell et al., 2010), adverse attitudes in regard to career aspirations, and a decrease in concentration and impairment in female cognitive performance (Kahalon, Shnabel, \& Becker, 2018; D. M. Quinn et al., 2011). Both romantic relationships and relationships in general have been studies in the context of objectification, but neither of these literatures have investigated specifically same-gender relationships.

There is evidence that the experience of state self-objectification in mixed-gender contexts (stranger and romantic) and within the self in any moment (trying on a swimsuit) has negative consequences, but what about in the context of interaction with other women? Is the self-objectification experience in mixed-gender interactions the same as that experienced in same-gender interactions? The ample research demonstrating that the male gaze has a particularly detrimental effect would suggest no (Gay \& Castano, 2010; Gervais, Vescio, \& Allen, 2011; Saguy, Quinn, F Dovidio, \& Pratto, 2010, p. Calogero (2004); Yilmaz \& Bozo, 2019). Women do objectify other women (Harsey \& Zurbriggen, 2020; Loughnan et al., 2015a; Puvia \& Vaes, 2013), but when they do it, does it lead to self-objectification in the same way men's objectification of women does (Garcia et al., 2016)? If so, does the self-objectification experienced in these same-gender interactions have the same negative consequences for authenticity in that interaction?

\#\#Interpersonal Objectification and Authenticity
There is some evidence that reduced authenticity is a consequence of self-objectification in the moment {[}Garcia et al. (2016); again CITE PWQ paper I reviewed, Yoder editor{]}. This link has been justified by the literature on stigmatized-stigmatizer interactions (CITE LITERATURE DIDN'T COME ACROSS THIS), viewing the experience of being objectified in an interaction as an identity threat situation (MAYBE CITE MILES-MCLEAN PAPER \enquote{STOP LOOKING AT ME!}). When a woman is objectified by a man, and then experiences self-objectification, this intergroup encounter might trigger identitiy threat, but is the same negative consequence present when a woman is objectified by another woman? woman-woman interpersonal objectification processes might diverge from this process. One the one hand, she may not be having the same negative consequences the cascade from situations that threated group-based identity (Deaux \& Major, 1987; Dovidio, Hebl, Richeson, \& Shelton, 2006; Hebl \& Dovidio, 2005), but feeling like a body, rather than a full human, in an interaction may be enough to reduce feelings of authenticity and social competence, regardless of the gender of the objectifyer {[}Tolman, Impett, Tracy, \& Michael (2006); PWQ paper I reviewed, Yoder editor{]}. I DONT KNOW WHERE THIS PAPER IS? ASK RANDI ABOUT IDENTITY\_THREAT PAPERS

\#\#The Current Study
In the current study, we sought to examine what occurs during an interaction in which one or both partners are objectifying each other, similarly to Garcia et al. (2016), but between same-sex female interpersonal interactions. Moreover, the current study uses a face-to-face interaction paradigm and dyadic data analysis techniques to examine the effects for both women simultaneously. We expected to replicate the results found in Garcia et al. (2016). We predicted that being objectified by one's interaction partner would lead to self-objectification, which in turn would lead to feelings of inauthenticity, then reduced feelings of agency in romantic relationships, reduced career aspiration, and reduced cognitive performance. Specifically, we expected to find a positive relationship between other-objectification by one's partner and state self-objectification. We also expect to find a negative relationship between self-state objectification and interaction authenticity, and that interaction authenticity will be positively related to cognitive performance, relationship agency, and career aspirations.

Puvia \& Vaes (2013) would alternatively predict that women's tendency to self-objectify (TSO) leads them to objectify other women (\ldots well, dehumanize a sexualized woman, but also Strelan \& Hargreaves (2005) would predict the TSO-\textgreater SOO link and Harsey \& Zurbriggen (2020) too), and this is mediated by the woman's own state self-objectification (SSO). So we also tested this as a possible alternative model.

\hypertarget{methods}{%
\section{Methods}\label{methods}}

\#\#Procedure
The procedure used was identical to that in Garcia et al. (2016), except for the instructions that the participants were given. In brief, that methodology is that each participant arrived at the laboratory and were then led into separate cubicles to prevent any communication between the participants before the interaction. In addition, each participant was screened for prior acquaintance to confirm that they had not met prior to the study. They were asked to sign the consent form to participate, and the study was described as follows: \enquote{This is a study looking at how students form different types of relationships at college.} A prompt on the computer screen told the participants that they were assigned to the \enquote{College Relationships} condition and gave the following instructions:

@@

\#\#Combined Samples

@@

\#\#Post interaction Measures

@@

\#\#\#Cognitive Performance

@@

\#\#\#State Other-Objectification

@@

\#\#\#Interaction Authenticity

@@

\#\#\#State Self-Objectification

@@

\#\#\#Relationship Agency

@@

\#\#\#Career Aspirations

To conceptualize participants' career aspirations after the interaction, we used the 10-item adaptation of P. Gray \& M. OBrien (2007)'s Career Aspiration Scale employed in Garcia et al. (2016), which asked participants to consider how true 10 statements were in regard to their future careers on a scale from 0 (not at all true of me) to 4 (very true of me). Items include \enquote{I hope to become a leader in my career field} and \enquote{I hope to move up through any organization or business I work in.} Items were fairly reliable (\(\alpha\) = 0.73 for Sample 1, \(\alpha\) = 0.80 for Sample 2).

\#\#\#Trait Self-Objectification

Trait self-objectification (TSO) was assessed using the Self-Objectification Questionnaire (Fredrickson et al., 1998; M. Noll \& L. Fredrickson, 1998), which evaluates the extent to which individuals view their bodies in observable versus non-observable ways. The questionnaire asked participants to rank order both appearance and functional aspects of their bodies, from 1 (least important) to 10 (most important), with respect to physical self-concepts. Of the ten body attributes, five of the items were appearance-based (weight, sex appeal, physical attractiveness, firm/sculpted muscles and body measurements), and five of the items were competence-based (strength, physical coordination, energy level, health and physical fitness). Difference scores were computed by subtracting the sum of the 5 functional aspects/competence attributes (e.g., health, strength) from the sum of the 5 physical self-concepts/appearance attributes (e.g., physical attractiveness, weight), and all measures were multiplied by -1, as was done in Garcia et al. (2016), so that positive scores indicated greater TSO.

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{data-analysis}{%
\subsection{Data analysis}\label{data-analysis}}

We used R (Version 3.6.2; R Core Team, 2017) and the R-packages \emph{apaTables} (Version 2.0.5; Stanley, 2018), \emph{devtools} (Version 2.2.2; Wickham et al., 2018b), \emph{dplyr} (Version 1.0.0; Wickham et al., 2018a), \emph{forcats} (Version 0.4.0; Wickham, 2018), \emph{ggformula} (Version 0.9.3; Kaplan \& Pruim, 2017), \emph{ggplot2} (Version 3.3.2; Wickham, 2016), \emph{ggstance} (Version 0.3.3; Henry et al., 2019), \emph{haven} (Version 2.2.0; Wickham \& Miller, 2019), \emph{irr} (Version 0.84.1; Gamer, Lemon, \& \textless puspendra.pusp22@gmail.com\textgreater, 2012), \emph{knitr} (Version 1.28; Xie, 2015), \emph{kutils} (Version 1.70; Johnson, Kite, \& Redmon, 2019), \emph{lattice} (Version 0.20.40; Sarkar, 2008), \emph{lavaan} (Version 0.6.7; Rosseel, 2012), \emph{lpSolve} (Version 5.6.15; Berkelaar \& others, 2015), \emph{Matrix} (Version 1.2.18; Bates \& Maechler, 2017), \emph{mosaic} (Version 1.5.0; Pruim, Kaplan, \& Horton, 2017, 2016), \emph{mosaicData} (Version 0.17.0; Pruim et al., 2016), \emph{nlme} (Version 3.1.144; Pinheiro, Bates, DebRoy, Sarkar, \& R Core Team, 2017), \emph{papaja} (Version 0.1.0.9842; Aust \& Barth, 2018), \emph{psych} (Version 1.9.12.31; Revelle, 2017), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2019), \emph{readr} (Version 1.3.1; Wickham et al., 2017), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.0.3; Müller \& Wickham, 2019), \emph{tidyr} (Version 1.0.2; Wickham \& Henry, 2019), \emph{tidyverse} (Version 1.3.0; Wickham, 2017), \emph{usethis} (Version 1.5.1; Wickham \& Bryan, 2018), and \emph{xtable} (Version 1.8.4; Dahl, Scott, Roosen, Magnusson, \& Swinton, 2019) for all our analyses.

\hypertarget{analysis-strategy}{%
\subsection{Analysis Strategy}\label{analysis-strategy}}
